Graph Exploration and Search

### 2017-11-10 exploratory.tex
Added some comment

Graph exploration entails that a user provided query on a graph is indefinite in nature, and therefore is likely to return either too few or too-many results. 
For this reason query reformulation techniques that aim at modifying the query to lead the user to the intended result have been proposed~\citep{mottin2015graph,hurtado2008query}. 
A \emph{reformulation} for a query $Q \subseteq G$ on a labeled graph $G = (V, E, \ell)$, with $\ell$ being a labeling function on nodes and edges, is a query $Q'$ that is either a supergraph or a subgraph of $Q$, $Q' \subseteq Q$ or $Q' \supseteq Q$. 
Therefore, $Q'$ can be more specific or more generic than $Q$. 
%For simplicity the graph is considered unlabeled, even though the presented methods work mostly with labeled graphs. 
%the set of $\mathcal{R}(Q)=\{G' \subseteq G | G' \equiv Q \}$ with a

Early attempts in this direction propose to enrich the SPARQL semantics with a \textsc{RELAX} clause that returns a set of reformulations following some predefined rules (such as expanding edges with a specific label)~\citep{hurtado2008query}.

%Few works explicitly target large graphs

>>>>

Graph exploration entails that a user provided query on a graph is indefinite in nature, and therefore is likely to return either too few or too-many results. 
For this reason query reformulation techniques that aim at modifying the query to lead the user to the intended result have been proposed~\citep{mottin2015graph,hurtado2008query}. 
A \emph{reformulation} for a query $Q \subseteq G$ on a labeled graph $G = (V, E, \ell)$ with labeling function on nodes and edges $\ell$, is a query $Q'$ that is either a supergraph or a subgraph of $Q$, $Q' \subseteq Q$ or $Q' \supseteq Q$. 
Therefore, $Q'$ can be more specific or more generic than $Q$. 
%For simplicity the graph is considered unlabeled, even though the presented methods work mostly with labeled graphs. 
%the set of $\mathcal{R}(Q)=\{G' \subseteq G | G' \equiv Q \}$ with a

Reformulation in graphs mostly involve collection on graphs or \emph{graph databases}.
\dnote{DAVIDE: GQRef~\citep{mottin2015graph}, Why-not on graphs\cite{islam2015efficient}}

Few works explicitly target large graphs.
Early attempts in this direction propose to enrich the SPARQL semantics with a \textsc{RELAX} clause that returns a set of reformulations following some predefined rules (such as expanding edges with a specific label)~\citep{hurtado2008query}.
